%{
	Created by Shehab Hesham.
%}
%Acknowledgements
\chapter*{Acknowledgments}

\par First and Foremost, I would like to thank Allah for the place I am in. \newline
\par Secondly, I would like to thank my supervisor, Dr. Moheb Mekhail, and the Dean of Engineering, Prof. Dr. Ashraf Zaher, for their constant support throughout this bachelor thesis duration. I would like to express my sincere gratitude for their expertise, mentorship, continuous encouragement, valuable guidance, support, and contributions throughout the development of this thesis. They have provided me with constructive feedback and helpful suggestions that have improved the quality of my work. \newline
\par Thirdly, I would like to thank all my lecturers, teaching assistants, and colleagues for all the information I have gained throughout the years in the engineering field. \newline %This could have not been possible without the GIU management. They have created a stimulating and inspiring learning environment that has enriched my academic experience. \newline
\par I would also like to thank anyone reading this for the time taken; I hope you find what you expect and gain as much information as possible. I appreciate your interest and attention to my research topic and I welcome any comments or questions you may have. \newline
\par I would also like to thank Eng. Amr Khalid, Dr. Hunter Adams, and Prof. Dr. Bruce Land for their valuable information that was made available to myself and others in need. They have shared their knowledge and expertise with me and have helped me to understand and implement the concepts and techniques involved in my project. \newline
\par I would like to express my heartfelt appreciation to my family, who have always been there for me throughout this journey. They have supported me with their care and encouragement, and have motivated me to pursue my dreams. I am truly grateful for having them in my life. \newline
\par Last but not least, I want to thank myself. I want to thank myself for believing in myself. I want to thank myself for doing all this hard work. I want to thank myself for having no days off. I want to thank myself for never quitting. I want to thank myself for always being a giver and trying to give more than I receive. I want to thank myself for trying to do more right than wrong. I want to thank myself for just being myself at all times. \newline
